# Reproducible Research: Peer Assessment 1
---
title: "First Assignment For Reproducible Research"
author: "Daqi Jiao"
date: "2015年8月15日"
output: html_document
---

## Loading and preprocessing the data

```{r}
activity <- read.csv("activity.csv")
head(activity)
```

## Calculating the mean total number of steps taken per day

```{r}
activity$date <- as.Date(activity$date, "%Y-%m-%d")
sum_per_day <- aggregate(steps ~ date, data = activity, sum, na.rm = TRUE)
hist(sum_per_day$steps, main = "Total steps by day", xlab = "day", col = "red")
mean(sum_per_day$steps)
median(sum_per_day$steps)
```

## Calculating average daily activity pattern

```{r}
time_series <- tapply(activity$steps, activity$interval, mean, na.rm = TRUE)
plot(row.names(time_series), time_series, type = "l", xlab = "5-min interval", ylab = "Averages across all days", main = "Daily activity pattern", col = "green")
max_interval <- which.max(time_series)
names(max_interval)
```

## Imputing missing values

```{r}
NA_number <- sum(is.na(activity))
print(NA_number)

steps_average <- aggregate(steps ~ interval, data = activity, mean)
fill_NA <- numeric()
for (i in 1:nrow(activity)) {
    obs <- activity[i, ]
    if (is.na(obs$steps)) {
        steps <- subset(steps_average, interval == obs$interval)$steps
    } else {
        steps <- obs$steps
    }
    fill_NA <- c(fill_NA, steps)
}

new_activity <- activity
new_activity$steps <- fill_NA

steps_total <- aggregate(steps ~ date, data = new_activity, sum, na.rm = TRUE)
hist(steps_total$steps, main = "Total steps by day", xlab = "day", col = "blue")
mean(steps_total$steps)
median(steps_total$steps)
```

## Identifying the differences in activity patterns between weekdays and weekends

```{r}
day <- weekdays(activity$date)
daylevel <- vector()
for (i in 1:nrow(activity)) {
    if (day[i] == "Saturday") {
        daylevel[i] <- "Weekend"
    } else if (day[i] == "Sunday") {
        daylevel[i] <- "Weekend"
    } else {
        daylevel[i] <- "Weekday"
    }
}
activity$daylevel <- daylevel
activity$daylevel <- factor(activity$daylevel)

stepsByDay <- aggregate(steps ~ interval + daylevel, data = activity, mean)
names(stepsByDay) <- c("interval", "daylevel", "steps")

xyplot(steps ~ interval | daylevel, stepsByDay, type = "l", layout = c(1, 2), 
    xlab = "Interval", ylab = "Number of steps")
```